---
title: "PROJECT IMDB ANALYSIS. DANA"
author: "Yamileth Hercules"
date: "2022-11-12"
output: pdf_document
---
#1 Reading the table and see the first columns

```{r }
imdb_ds <-read.csv('../data/imdb_top_1000.csv', header = TRUE,  na.string = c(""))
head(imdb_ds)
```
# Looking the dimensions of the table
```{r}
dim(imdb_ds)
```


# Looking the data type
```{r}
str(imdb_ds)
```

# Subsetting the variables.

```{r}
subset_imdb <- imdb_ds[, -c(1,8,9,11,12,13,14)]
subset_imdb 
```
# Looking the dimesions of my subset of data set 
```{r}

dim(subset_imdb)
```

# Looking the variables with missing values 

```{r}

sum(is.na(subset_imdb))
summary(subset_imdb)
```

# Observing the data carefully

There is an error in the the column Released Year in the dataset and it is going to be replace with the value with more frecuency

```{r}

unique(subset_imdb$Released_Year)

```


```{r}
subset_imdb$Released_Year[subset_imdb$Released_Year == 'PG'] <- '1995'
unique(subset_imdb$Released_Year)
View(subset_imdb)
```

# How many movies are made per year (ranges) in the top 1000 IMDB? 

#Making the year as numerical variable

```{r}

Realesed_year_variable <- strtoi(subset_imdb$Released_Year)

```


generating the frecuency table for the variable
```{r}

min<- min(subset_imdb$Released_Year)
max<- max(subset_imdb$Released_Year)
ry_table <- table(cut(Realesed_year_variable, breaks = seq(min, max, by =9)))
ry_table


```


```{r}

barplot(ry_table, ylab = "Frequency", xlab = 'Released Year in ranges', main = "MOVIES PER YEAR", col='steelblue')
?barplot
```

Taking the variable as a numerical variable and generating a Histogram 
```{r}
histo <- hist(Realesed_year_variable, breaks = 30, col='steelblue', xlab = 'Released Year', main = "MOVIES PER YEAR")
?hist
```
# Conclusion:

The distribution has negative skewness. The graph shows that there is an upward trend in the list of the best 1000 movies. Since the year 2000 the number has increased to more than 100 films in the mentioned list.  

```{r}
boxplot(Realesed_year_variable, horizontal=TRUE, col='steelblue')
?boxplot
```

#Conclusion:
The boxplot clearly shows that the distribution is skewed to the left. The mean is approximately close to the year 2000. It also shows some extreme values before the minimum percentile.


```{r}
 library(dplyr)

director_table <- table(subset_imdb$Director)
director_table <-tail(sort(director_table),10)
director_table

```


```{r}
barplot(director_table, ylab = "Frequency", xlab = 'Director most Prolific', main = 'Director', col=c('steelblue','yellow', 'orange','green', 'beige', 'violet','brown','pink', 'red','gray'), legend.text = rownames(director_table))

```


---> Bivariate statements:

- What is the correlation between votes and IMDB rating? (Numerical variables: Number_of_votes and IMDB rating)

## Correlation analysis:

```{r}
plot(subset_imdb$No_of_Votes, subset_imdb$IMDB_Rating, xlab = 'No of votes', ylab = 'IMDB Rating')
fit = lm(subset_imdb$IMDB_Rating ~ subset_imdb$No_of_Votes)
abline(fit)
```


```{r}
cor(subset_imdb$No_of_Votes, subset_imdb$IMDB_Rating)
```

CONCLUSION: There is a positive low correlation between the variables, there are some outliers.
 
 
---> Test for the significance correlation to verify if this correlation applies to the population or just to the sample:

- Null hypothesis: The number of votes and the IMDB rating do not have linear correlation among all subjects in the population
- Alternative hypothesis: The number of votes and the IMDB rating have linear correlation among all subjects in the population

n = 1000
r = 0.4949
DP < 0.139

In this case r > DP, therefore, the x and y variable have positive linear relation among all subjects in the population so we have enough statistical evidence to reject the null hypothesis.

## Regression analysis:

```{r}
summary(fit)
```

Formula: y = mx + b
           = 4.164(x)+7.835

## Verify: Intercept -> When one movie does not have audience votes, the intercept does not have meaning because the IMDB rating depends on the number of votes.
## verify: Slope -> When the number of votes varies X units, the movie is going to change 4.16 unites in the IMDB Rating.

## Validate the adequacy of the linear fit:

1. Linearity and Homoscedasticity conditions:

```{r}
plot(subset_imdb$No_of_Votes, fit$residuals, xlab = 'No of votes', ylab = 'Residuals')
abline(h = c(-0.4, 0, 0.6), col= c('blue', 'red', 'blue'), lty= c(2, 1, 2), lwd= c(3, 2, 3))
abline(h=0)
```


### Verify: We consider that the linear and homoscedaticity conditions are valid because the values are distribuited in the plot and they do not show any pattern.

2. Normal condition:

```{r}
hist(fit$residuals, xlab = 'Residuals')
```

## Verify: The normal condition is valid because the residuals follow a Normal Distribution despite being slightly skewed to the right.


